### 2014-07-20 docs/paper/text/solution.tex
added ILP solution for the overlapping case

%$\mathcal{P}(B) \leftarrow \emptyset$ \tcp*{Initial partitioning}

\subsection{Mixed Integer Linear Program Formulation}
$x_{a,p}$: $1$ if attribute $a$ is in partition $p$, $0$ otherwise.\\
$y_{p,q}$: $1$ if partition $p$ is used by query $q$, $0$ otherwise.\\
$z_{a,p,q}$: $1$ if partition $p$ is used by query $q$, and attribute $a$ is in partition $p$, $0$ otherwise.\\
$u_{p}$: $1$ if partition $p$ is assigned at least $1$ attribute, $0$ otherwise.\\

@@

% NOTE: In the simulation we will have query weights that will factor into the objective function
\begin{eqnarray}
\text{minimize}  
    \sum_{q\in Q} \sum_{p=1}^{k} && (16\cdot c_e(B) + 12\cdot c_n(B))\cdot y_{p,q}\nonumber\\
    &+& \sum_{a\in A} s(a)\cdot c_e(B)\cdot z_{a,p,q} \nonumber\\
\text{subject to}&&\nonumber\\
\forall_{a\in A}, 
    && \sum_{p=1}^{k} x_{a,p} = 1\nonumber\\
\forall_{\{p,q\}\in [1..k]\times Q}, 
    &&  \sum_{a\in A} q(a)\cdot x_{a,p} - y_{p,q} \geq 0 \nonumber\\
\forall_{\{p,q\}\in [1..k]\times Q}, 
    &&  K\cdot y_{p,q} - \sum_{a\in A} q(a)\cdot x_{a,p}  \geq 0 \nonumber\\
\forall_{\{a,p,q\}\in A\times [1..k]\times Q},
    && z_{a,p,q} - (x_{a,p} + y_{p,q}) \geq -1\nonumber\\
\forall_{p\in[1..k]},
    && \sum_{a\in A} x_{a,p} - u_p \geq 0 \nonumber\\
\forall_{p\in[1..k]},
    && K\cdot u_p - \sum_{a\in A} x_{a,p} \geq 0 \nonumber\\    
 && \sum_{p=1}^{k} u_p -1 \leq \frac{\alpha}{
1-\frac{c_e(B)\cdot \sum_{a\in A} s(a)}{s(B)}
 } \nonumber
\end{eqnarray}

@@

@@

>>>>

\subsubsection{Mixed Integer Linear Program Formulation}
$x_{a,p}$: $1$ if attribute $a$ is in partition $p$, $0$ otherwise.\\
$y_{p,q}$: $1$ if partition $p$ is used by query $q$, $0$ otherwise.\\
$z_{a,p,q}$: $1$ if partition $p$ is used by query $q$, and attribute $a$ is in partition $p$, $0$ otherwise.\\
$u_{p}$: $1$ if partition $p$ is assigned at least $1$ attribute, $0$ otherwise.\\

@@

% NOTE: In the simulation we will have query weights that will factor into the objective function
\begin{eqnarray}
\text{minimize}  
    \sum_{q\in Q} \sum_{p=1}^{k} && (16\cdot c_e(B) + 12\cdot c_n(B))\cdot y_{p,q}\nonumber\\
    &+& \sum_{a\in A} s(a)\cdot c_e(B)\cdot z_{a,p,q} \nonumber\\
\text{subject to}&&\nonumber\\
\forall_{a\in A}, 
    && \sum_{p=1}^{k} x_{a,p} = 1\nonumber\\
\forall_{\{p,q\}\in [1..k]\times Q}, 
    &&  \sum_{a\in A} q(a)\cdot x_{a,p} - y_{p,q} \geq 0 \nonumber\\
\forall_{\{p,q\}\in [1..k]\times Q}, 
    &&  K\cdot y_{p,q} - \sum_{a\in A} q(a)\cdot x_{a,p}  \geq 0 \nonumber\\
\forall_{\{a,p,q\}\in A\times [1..k]\times Q},
    && z_{a,p,q} - (x_{a,p} + y_{p,q}) \geq -1\nonumber\\
\forall_{p\in[1..k]},
    && \sum_{a\in A} x_{a,p} - u_p \geq 0 \nonumber\\
\forall_{p\in[1..k]},
    && K\cdot u_p - \sum_{a\in A} x_{a,p} \geq 0 \nonumber\\    
&& \sum_{p=1}^{k} u_p -1 \leq \frac{\alpha}
  {1-\frac{c_e(B)\cdot \sum_{a\in A} s(a)}{s(B)}} \nonumber
\end{eqnarray}

@@

\subsubsection{Heuristic Solution}

\paragraph*{Approach.} TODO

@@

\subsubsection{Mixed Integer Linear Program Formulation}
% NOTE: In the simulation we will have query weights that will factor into the objective function
\begin{eqnarray}
\text{minimize}  
    \sum_{q\in Q} \sum_{p=1}^{k} && (16\cdot c_e(B) + 12\cdot c_n(B))\cdot y_{p,q}\nonumber\\
    &+& \sum_{a\in A} s(a)\cdot c_e(B)\cdot z_{a,p,q} \nonumber\\
\text{subject to}&&\nonumber\\
\forall_{a\in A}, 
    && \sum_{p=1}^{k} x_{a,p} > 0\nonumber\\
\forall_{a\in A}, 
    && \sum_{p=1}^{k} x_{a,p} \leq k\nonumber\\
\forall_{\{a,q\}\in A\times Q},
    &&  \sum_{p=1}^{k} z_{a,p,q} \geq q(a) \nonumber\\
\forall_{\{p,q\}\in [1..k]\times Q}, 
    &&  \sum_{a\in A} z_{a,p,q} - y_{p,q} \geq 0 \nonumber\\
\forall_{\{p,q\}\in [1..k]\times Q}, 
    &&  K\cdot y_{p,q} - \sum_{a\in A} z_{a,p,q}  \geq 0 \nonumber\\
\forall_{\{a,p,q\}\in A\times [1..k]\times Q}, 
    && z_{a,p,q} - (y_{p,q} + q(a)) \geq -1 \nonumber\\
\forall_{p\in[1..k]},
    && \sum_{a\in A} x_{a,p} - u_p \geq 0 \nonumber\\
\forall_{p\in[1..k]},
    && K\cdot u_p - \sum_{a\in A} x_{a,p} \geq 0 \nonumber\\    
&& \sum_{p=1}^{k} u_p -1 \leq \frac{\alpha}
  {1-\frac{c_e(B)\cdot \sum_{a\in A} s(a)}{s(B)}} \nonumber
\end{eqnarray}

\subsubsection{Heuristic Solution}
